Study of Illumination Dependency in the Dynamic Laser Speckle Analysis

### 2020-01-23 article/article_1.tex
revision de contnido antes de revisar ingles

@@

In the ink drying test, 
we analyzed the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
by the separation of the signals in different frequency bands;
when there was a process that changes its behavior over time.

In the paper piece test, we considered that none material is completely inert and, consequently, 
the observed signal  in the  dynamic speckle analysis has more than noise.

By the analysis shown in the Figs. \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
we can observe that the greater the laser illumination level $\mu_p$, 
the greater the range of speckle light intensity variation $\sigma_p$ of each pixel analyzed, 
however this increase depend of speckle signal frequency band analyzed.
This is reaffirmed by the analysis of the ink drying test, 
seen in the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
where the curves of regions with high and low luminosity are compared.

Thus, by the results shown in the Figs. \ref{fig:numerical} and \ref{fig:papelilllevel},
we can theorize that this augmentative effect of the dynamic range in the speckle, acts predominantly on speckle signals with low frequency components, and in smaller predominance on speckle signals with high frequency components. 
This hypothesis is supported by other works with similar results \cite{Nothdurft:05},
where the temporal speckle mean matrix shows information about the surface of sample and the laser illumination level, and the temporal speckle deviation matrix shows information of material inside at different levels and in less proportion the information of the laser illumination level.
Given that the mean value collect information of zero frequency component in the speckle signal, 
and the standard deviation  collect information of non-zero frequency components.
We can make a parallel, with the results obtained in the present work,
and thus  to indicate that the speckle signals with frequency components with greater value are less affected in their dynamic range by the variation of the laser light intensity.
By analyzing the index Fujii, we also highlight that generalizations cannot be made for all speckle indices.
In this work we mainly use the standard deviation, because its calculation is directly linked to the value, or amplitude, root mean square of the signals.
In counter-parted, the Fujii index makes a previous filtering and a non-linear scaling with respect to the light intensity, which hinders a fair interpretation, of its behavior for different frequency bands.

Thus, in this work were presented comparisons between the values of the temporal speckle deviation index for three different frequency bands of the speckle signal and different illuminations levels, 
in a dynamic laser speckle analysis. 
The results showed that the influence of the illumination level in a DLSI, 
like the temporal speckle deviation index, 
decreases with the use of signals with high frequency components.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Final comments}

By the results shown in the Figs. \ref{fig:numerical} and \ref{fig:papelilllevel},
we can theorize that the dynamic range,
between the samples with greater and  less values, 
in  the temporal speckle deviation index,
they are greater on speckle signals with low frequency components, 
and  smaller on speckle signals with high frequency components;
thus, we can observe that the effect of illumination level in 
the variability of the temporal speckle deviation index decrease with the frequency.
This hypothesis is supported by other works with similar results \cite{Nothdurft:05},
where the temporal speckle mean matrix shows information about the surface of sample and the laser illumination level, 
and the temporal speckle deviation matrix shows information of material inside at 
different levels and in less proportion the information of the laser illumination level.
Given that the mean value collect information of zero frequency component in the speckle signal, 
and the standard deviation  collect information of non-zero frequency components.
We can make a parallel, 
with the results obtained in the present work,
and thus  to indicate that the speckle signals with high frequency components
 are less affected in their dynamic range by the variation of the laser light intensity.
By analyzing the index Fujii, 
we also highlight that generalizations cannot be made for all speckle indices.
In this work we mainly use the standard deviation, because its calculation is directly linked to the value, 
or amplitude, root mean square of the signals.
In counter-parted, the Fujii index makes a previous filtering (subtract a sample with the previous one) 
and a non-linear scaling with respect to the light intensity (divide by the average intensity between two consecutive samples), 
which hinders a fair interpretation, of its behavior for different frequency bands.

@@

In the ink drying test, 
we analyzed a process that changes its behavior over time,
and we seen the effect produced in  the speckle light intensity, 
and consequently in the standard deviation index, 
by the separation of the signals in different frequency bands.
By other side, in the paper piece test, 
we considered that none material is completely inert and, consequently, 
the observed signal  in the  dynamic speckle analysis has more than noise.

%% Mayor quantidade de luz, mayor sigma index
By the analysis of paper piece shown in the Figs. \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
we can see that the greater the observable laser illumination level $\mu_p$, 
the greater will the $\sigma_p$ index of each pixel analyzed, 
however this increase depend of frequency band in the speckle signal  analyzed;
by example, in the Fig. \ref{fig:illlevel_stdz},
with high frequency components, the relation between $\mu_p$ and $\sigma_p$ its almost a horizontal line, 
this mean that the variation of $\mu_p$ no affect significantly to the $\sigma_p$ index.
This is reaffirmed by the analysis of the ink drying test, 
seen in the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
where the curves of regions with high and low luminosity are compared in different frequency bands,
being the case with high frequency band  (Fig. \ref{fig:stdzink}) 
the one that produces very similar indices, despite the difference in the illumination level.

Thus, in this work were presented comparisons between the values of the temporal 
speckle deviation index for three different frequency bands of the speckle signal and 
different illuminations levels in a dynamic laser speckle analysis. 
The results showed that the influence of the observable illumination level in a DLSI, 
like the temporal speckle deviation index, 
decreases with the use of signals with high frequency components.
